Spatial and temporal decay of SARS-CoV-2 environmental contamination of the healthcare environment

### 2021-12-09 manuscript.Rmd
Add roboto font.

---
#title: "Spatial and temporal effects on SARS-CoV-2 contamination of the healthcare environment"
#author: "Brendan J. Kelly, MD, MS"
bibliography: bib/references.bib
csl: csl/infection-control-and-hospital-epidemiology.csl
output: html_document
css: style_helvetica_double.css
---

>>>>

---
#title: "Spatial and temporal effects on SARS-CoV-2 contamination of the healthcare environment"
#author: "Brendan J. Kelly, MD, MS"
bibliography: bib/references.bib
csl: csl/infection-control-and-hospital-epidemiology.csl
output: html_document
css: style_roboto_double.css
---
